The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-10 writing/draft3/draft11.tex
asd

Besides our main model, we estimated the same specification for two additional subsamples of Kenyan counties. In particular, we estimated the model for the subsample of ASAL counties and for the subsample of non-ASAL counties separately to compare the effects of various weather characteristics across the two areas with significantly different climate. The estimates of all three models are summarised in table \ref{MainEst}. The first two columns represent the model for all counties,  the third and fourth columns include estimates based on the ASAL counties and the last two columns describe the estimates based on the subsample of the non-ASAL counties. Besides the coefficient estimates, we present measures of relative importance of the predictors. These can be found in the columns denoted F-value in table~\ref{MainEst}.

Consistently with our assumptions, 
Besides seasonal precipitation and average temperature, the length and number of dry spells

>>>>

Besides our main model, we estimated the same specification for two additional subsamples of Kenyan counties. In particular, we estimated the model for the subsample of ASAL counties and for the subsample of non-ASAL counties separately to compare the effects of various weather characteristics across the two areas with significantly different climate. The estimates of all three models are summarised in table~\ref{MainEst}. The first two columns represent the model for all counties, the third and fourth columns include estimates for the subsample of ASAL counties and the last two columns describe the estimates based on the subsample of non-ASAL counties. All the predictors were standardised, therefore the estimates and the corresponding p-values can be interpreted as measures of relative importance. As an additional measure of relative importance we included F-values of the type \textit{III} analysis of variance in table~\ref{MainEst}. The F-tests were conducted using the marginal rather than sequential sum of squares. That is, for each variable, the F-test is a test of significance of that part of explained sum of squares which can be contributed to the particular explanatory variable. In other worlds, the F-value is a test statistic of comparison of the preferred model (with all variables in table~\ref{MainEst}) and the model without the explanatory variable in question but including all other predictors of the preferred model.

The models have a log-linear functional form, therefore estimates in table~\ref{MainEst} are not directly interpretable as marginal effects and their effect on yields is multiplicative. As in the classical linear regression model, a negative sign implies a negative effect and positive sign is consistent with positive effect on maize yield.
We will first discuss the estimates for the sample of all counties, that is the first two columns of table~\ref{MainEst}, then we will describe the models of the two subsamples.   Consistently with our assumptions, seasonal precipitation has positive and significant effect on maize yields while average temperature has negative effects on yields for the case of all counties.  The squared seasonal precipitation has negative effect, but...marginal total effect

affects the

Besides seasonal precipitation and average temperature, the length and number of dry spells
